Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-05-21 manuscript.Rmd
Comments

```{r message=FALSE, include=FALSE, results='hide'}
library(tidyverse)
library(lme4)
library(lmerTest)
library(rio)
```

@@

sjPlot::tab_model(SRMdat1)
```

>>>>

```{r message=FALSE, include=FALSE, results='hide'}
library(tidyverse)
library(lme4) #Don't know why, but this wasn't immediately working
library(lmerTest)
library(rio)
```

@@

sjPlot::tab_model(SRMdat1) #this is really cool
```
